### 2013-02-16 doc/icml2013/discussion.tex
edit

\section{Discussion}
\label{sec:discussion}

Role of spectral algorithms in discriminative tasks.

Challenges and ways forward?

>>>>

\section{Conclusion}
\label{sec:conclusion}

In this paper, we developed a computationally efficient and statistically
consistent estimator for mixture of linear regressions, a first step at
tackling discriminative latent-variable models.  Our algorithm, Specral
Experts, regresses on higher-order powers of the data with a regularizer that
encourages low rank structure, followed by tensor factorization to recover the
actual parameters.  Empirically, Spectral Experts generally does not outperform
EM, but when used to initialize EM, yields significantly more accurate and
stable results than EM.

### 2013-02-16 doc/icml2013/intro.tex
edit

% Results
The result is a simple and efficient two-stage algorithm,
which we call Spectral Experts.
We prove that our algorithm yields consistent parameter estimates under certain
new identifiability conditions.  We also conduct an empirical evaluation
of our technique to understand its statistical properties (\sectionref{sec:evaluation}).
In particular, we find that in the low data regime,
Spectral Experts underperforms EM due to its weaker statistical efficiency,
but in the high data regime,
Spectral Experts outperforms EM.
We get the best results by using Spectral Experts as an initialization
to EM.

>>>>

% Results
The result is a simple and efficient two-stage algorithm,
which we call Spectral Experts.
We prove that our algorithm yields consistent parameter estimates under certain
new identifiability conditions.  We also conduct an empirical evaluation
of our technique to understand its statistical properties (\sectionref{sec:evaluation}).
%In particular, we find that in the low data regime,
%but in the high data regime,
%Spectral Experts outperforms EM.
While Spectral Experts generally does not outperform EM, presumably due to its
weaker statistical efficiency, it serves as an effective initialization for EM,
significantly outperforming EM with random initialization.
